### 2020-06-08 sections/magic/magic.tex
Reshuffling section IV

Magic states are necessary for achieving universal quantum computation within fault-tolerant schemes.
Identifying magic as a resource for quantum universality has led to several theories which try to provide a framework for its quantification and manipulation \nick{CITE}.
The main question that such a theory attempts to answer is:
\begin{center}
    \emph{Given two magic states $\rho$ and $\rho'$ is there a free operation that can convert $\rho$ to $\rho'$?}
\end{center}
Magic monotones are often used \nick{CITE} to partially address this question, although such approaches do not exploit much of the structure of the theory.
Therefore, we introduce a generalised notion of a measure, the \emph{fragment}, applicable in general resource theories and in particular in all theories of magic we consider. \nick{expand}

We are interested in all resource theories of magic $\R = (\F, \O)$ that obey two assumptions:
\begin{enumerate}[I]
    \item Free operations send free states into free states, $\E: \F \mapsto \F$, for all $\E \in \O$;
    \item Resource theory $\R$ is a completely free state preserving theory, in the sense that for any $d$-dimensional ancilla system and all free operations $\E$, $(\id_d \otimes \E ) \sigma \in \F$ whenever $\sigma \in \F$.
\end{enumerate}
The first assumption simply states that resources cannot be generated for free and is a minimal requirement for a resource theory. 
An immediate consequence is that if statistical mixing is included in $\O$, then the resource theory is convex.
Convex resource theories have attracted a lot of attention recently \nick{CITE} and include the magic theories discussed in~\cref{sec:prev}.
The second assumption implies that resources cannot be generated even when ancillas are allowed \nick{example of T state generation on Bell state by Campbell}.

The main result of this paper is that any magic theory $\R$ satisfying the above assumptions can be recast as a subtheory of stochasticity.
This reformulation grants additional power to the theory as the structure of stochastic process can be exploited to add insight to the main questions of theories as stated above. \nick{expand}

@@

Even though non-stabilizerness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable in~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
The Wigner distribution of a state in odd prime dimensions is discussed rigorously in~\cref{sec:wigner} and arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{cit:howard2, cit:veitch2}.
In this framework, the stabilizer states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabilizer states~\cite{cit:gross}.
Therefore, stabilizer-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{cit:wang}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
Informally, it can be considered as the maximal theory of magic $\R_{\rm{max}} = (\F_{\rm{max}}, \O_{\rm{max}})$, where free states have non-negative Wigner distributions and free operations completely preserve this property.

>>>>

Magic states are necessary for achieving universal quantum computation within fault-tolerant schemes.
Identifying magic as a resource for quantum universality has led to several theories which try to provide a framework for its quantification and manipulation \nick{CITE}.
The main question that such a theory attempts to answer is:
\begin{center}
    \emph{Given two magic states $\rho$ and $\rho'$ is there a free operation that can convert $\rho$ to $\rho'$?}
\end{center}

We are interested in all resource theories of magic $\R = (\F, \O)$ in which free operations cannot generate any amount of resource. 
The structure of such theory is described by a pre-order, often called partial order \nick{CITE}, $\prec_{\R}$ between states.
We write $\rho' \prec_{\R} \rho$ iff there exists $\E \in \O$ such that $\E(\rho) = \rho'$.
Naturally, states may be incomparable under the given theory, meaning that there exists no free operation that converts one to the other.

Formally, the no resource generation condition on the theories translates into two assumptions:
\begin{enumerate}[I]
    \item Free operations send free states into free states, $\E: \F \mapsto \F$, for all $\E \in \O$;
    \item Resource theory $\R$ is a completely free state preserving theory, in the sense that for any $d$-dimensional ancilla system and all free operations $\E$, $(\id_d \otimes \E ) \sigma \in \F$ whenever $\sigma \in \F$.
\end{enumerate}
The first assumption simply states that resources cannot be generated for free and is a minimal requirement for a resource theory. 
An immediate consequence is that if statistical mixing is included in $\O$, then the resource theory is convex.
Convex resource theories have attracted a lot of attention recently \nick{CITE} and include the magic theories discussed in~\cref{sec:prev}.
The second assumption implies that resources cannot be generated even when ancillas are allowed \nick{example of T state generation on Bell state by Campbell}.

Monotones are often used \nick{CITE} to address the question of state convertibility, although such approaches are usually generic.
A monotone of any general resource theory is a projection of the theory onto the non-negative real numbers, collapsing the pre-order of the theory to the total order defined on the real line.
This is the \nick{most naive} non-trivial projection under which the images of incomparable states can be compared.
Our first contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure.
Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
We show that a magic theory can be subdivided into \emph{fragments} \nick{expand}

@@

Even though non-stabilizerness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable in~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
The Wigner distribution of a state in odd prime dimensions is discussed rigorously in~\cref{sec:wigner} and arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{cit:howard2, cit:veitch2}.
In this framework, the stabilizer states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabilizer states~\cite{cit:gross}.
Therefore, stabilizer-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{cit:wang}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.

### 2020-06-08 sections/magic/phasespace.tex
Reshuffling section IV

We can define the phase-point operators,
\begin{align}
	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \pd} \omega^{\bmx \wedge \bmz} D_{\bmz},\ \bmx \in \pd. \label{eq:ax}
\end{align}
\nick{$\wedge$ has not be defined} They form an orthogonal Hermitian operator basis.
Therefore, any quantum state $\rho \in \cal{B}(\hd)$ can be expressed as a linear combination of the phase-point operators,
\begin{equation}
    \rho = \sum_{\bmz \in \pd} \W[\bmz]{\rho} A_{\bmz},
\end{equation}
where the coefficient vector $\W{\rho}$ is the Wigner distribution of state $\rho$,
\begin{equation}\label{eq:wstate}
    \W[\bmx]{\rho} \coloneqq \frac{1}{d}\tr[A_{\bmx} \rho].
\end{equation}
It is in fact a bounded $d^2$-dimensional quasi-probability distribution over $\pd$ as shown in~\cref{app:wigner}.

@@

The particular form of~\cref{eq:woperation} was chosen so that Wigner distributions of operations act as transition matrices for Wigner distribution of states, $\W{\E(\rho)} = \W{\E}\W{\rho}$.
In particular, $\cptp$ operations that map a Hilbert space to itself and have non-negative Wigner distributions correspond to stochastic matrices.
All these properties are shown in~\cref{app:wigner}

@@

Equipped with the definitions of the Wigner distribution, we can formally define the Wigner positivity theory $\R_{\rm{max}}$ in odd prime dimensions.
The free states are all states with non-negative Wigner distributions 
\begin{equation}
    \F_{\rm{max}} \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \pd\}
\end{equation}
The free operations should send the set of free states $\F_{\rm{max}}$ into itself and completely preserve the non-negativity of the states, in the sense that $\E \in \O_{\rm{max}}$ iff $(\id_d \otimes \E ) \sigma \in \stab$ for all odd prime dimensions $d$ whenever $\sigma \in \F_{\rm{max}}$.

It is shown by Wang \textit{et al.}~\cite{cit:wang} that $\O_{\rm{max}}$ coincides with the set of operations $\E$ with a non-negative Wigner distributions, 
\begin{equation}
    \O_{\rm{max}} = \{ \E: \W[\bmy|\bmx]{\E} \geq 0 \text{ for all } \bmx, \bmy \in \pd\}.
\end{equation}

>>>>

We can define the phase-point operators,
\begin{align}
	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \pd} \omega^{\bmx \wedge \bmz} D_{\bmz},\ \bmx \in \pd. \label{eq:ax}
\end{align}
\nick{$\wedge$ has not be defined} They form an orthogonal Hermitian operator basis.
Therefore, any quantum state $\rho \in \cal{B}(\hd)$ can be expressed as a linear combination of the phase-point operators,
\begin{equation}
    \rho = \sum_{\bmz \in \pd} \W[\bmz]{\rho} A_{\bmz},
\end{equation}
where the coefficient vector $\W{\rho}$ is the Wigner distribution of state $\rho$,
\begin{equation}\label{eq:wstate}
    \W[\bmx]{\rho} \coloneqq \frac{1}{d}\tr[A_{\bmx} \rho].
\end{equation}
It is in fact a real, bounded, $d^2$-dimensional quasi-probability distribution over $\pd$ as shown in~\cref{app:wigner}.

@@

The specific form of~\cref{eq:woperation} is chosen so that Wigner distributions of operations act as transition matrices for Wigner distributions of states, $\W{\E(\rho)} = \W{\E}\W{\rho}$.
In particular, $\cptp$ operations that map between density operators of equal dimensions and have non-negative Wigner distributions correspond to stochastic matrices, as shown in~\cref{app:wigner}

@@
